IGRINS spectra of \name

### 2016-05-05 document/ms.tex
Write club with Katelyn on Thursday May 5: ticking off outline items.

\subsection{Challenges: Tuning the transition probability matrix}
\label{sec:MC-challenges}

@@

Figure XX shows the data of XX plotted from the interval X-Y.  Our IGRINS observation dates of Z and Q show that the spectra were probably acquired during a phase of XX.  The ESPaDoNs spectra were at a phase of Z, indicating...

@@

@@

We compared the IGRINS spectrum of \name to the \PHOENIX grid of pre-computed synthetic model spectra \citep{2013A&A...553A...6H}.

We modified the default implementation by chunking the spectrum into 58 of its cleanest spectral orders and deriving the stellar parameters $\vt_{\ast,m}$ \emph{independently} in each $m^{\mathrm{th}}$ order.  We therefore have 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.  The figure shows a dramatic effect: \textbf{The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.}

We interpret the cooler temperatures derived at $K-$band as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.  Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.  We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).

@@

@@

@@

>>>>

@@

Figure XX shows the ASASSN X-band monitoring plotted from the interval X-Y.  Our IGRINS observation dates of Z and Q show that the spectra were probably acquired during a phase of XX.  The ESPaDoNs spectra were at a phase of Z, indicating...

We fit all the data in the interval X to Z in the following way:

@@

\subsection{Result 11}
We expect that applying approach 11 (single component to all orders , \iancze) is a poor model for our multicomponent stellar data and would therefore yield a poor quality fit.  Nevertheless we experimented with a single temperature fit to $N_{ord}=X$ IGRINS spectral orders with X samples sampling Theta and Phi parameters in the blocked Gibbs sampler identically to \iancze.  We found relatively poor fit quality, with large typical residuals of X.  The poor fit is exemplified in the top panel of Figure X which shows the observed spectrum in the region of the X line.  The best fit model with theta = [x, y, z] does not achieve a good fit of the X line.

@@

We chunked the IGRINS spectrum into $N_{ord}=$58 of its cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.  We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.  The figure shows a dramatic effect: \textbf{The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.}

@@

Figure XX shows the joint posterior probability density distribution of $\teffb$ versus $f$ calculated independently for $N_{ord}=25$ IGRINS orders.

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/Star_spot_measurement} 
	\caption{Effective temperature as derived by different orders.}
	\label{fig:StarspotProperties}
\end{figure*}

@@

We interpret the cooler temperatures derived at $K-$band in Approach 12 as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.  Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.  We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).

The systematically different teffs seen in Approach 12 could also be attributable to magnetic fields (cite XX).

@@

\section{Challenges: Tuning the transition probability matrix}
\label{sec:MC-challenges}
